### 2015-03-26 tex/proofs.tex
Cleaned up the reference-equals proof, as well as miscellaneous other problems in proofs.tex. Commented out problems in Definitions.tex

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\gse$ and
$s_\sym$, are related in the bisimulation, $s_\gse \sqsubset
s_\sym$, every successor, from either state, $s_\gse
\rgse s_\gse^\prime$ or $s_\sym \rsym
s_\sym^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\gse^\prime \sqsubset s_\sym^\prime$.

@@

\begin{theorem}

\end{theorem}

%\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
%\label{lem:init}
%If $s_\sym \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $s_\sym = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $s_\sym^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
% $$s_\sym^\prime \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
%\end{lemma}

@@

Now, to prove the reverse direction, choose any state $\gsest^\prime$ such that $\gsest^\prime \sqsubset q^\prime$. Since $\gsest^\prime \sqsubset q^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $\gsest^\prime \rightharpoonup_{h^\prime} q^\prime$, and that $\mathbb{S}( \phi_\gsest^\prime \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h^\prime} q^\prime) )$. From state $\gsest^\prime$, construct state $\gsest$ such that 
\begin{align*}
\gsest &= \lp \cfgnt{L}_\gsest\ \cfgnt{R}_\gsest\ \phi_\gsest\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
L_\gsest &= L_{\gsest^\prime} \setminus \{\cfgnt{r}^\prime \}\\
R_\gsest &= R_{\gsest^\prime}\\
\phi_\gsest &= \phi_\gsest^\prime
\end{align*}
Observe that by virtue of the GSE Field Access rule, $\gsest \rgse \gsest^\prime$. Now, construct function $h_\gsest$ so that $h_\gsest = h^\prime$. Observe that by Definition~\ref{def:homomorphism} $\gsest \rightharpoonup_{h_\gsest} q$,  and that $\mathbb{S}( \phi_\gsest \wedge \mathbb{HC}(\gsest \rightharpoonup_{h_\gsest} q) )$, so $\gsest \sqsubset q$. Therefore:
\begin{equation}
\forall q^\prime ( q \rsym q^\prime\Rightarrow \exists \Gsest^\prime( (\Gsest \rsgse \Gsest^\prime )\wedge (\Gsest^\prime\ \sqsubset\ q^\prime ))  )
\end{equation}
 This concludes the proof.
\end{proof}

%proof for field write
%\begin{lemma}[Exactness of Field Write Rule]
%\label{lem:write}
%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{FW}$ and $s_\gse \sqsubset s_\sym$, then:
%\begin{equation}
%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%\end{lemma}

@@

@@

\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
\label{lem:FA-determ}
Given a state, $s$, with a deterministic heap,
$(\cfgnt{L}\ \cfgnt{R}) =
\mathrm{heap}(s)$, the new heap,
$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
\mathrm{heap}(s^\prime)$, in any state related by the field
access rule, $s \rightarrow_\mathit{FA} s^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
\label{lem:FW-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the field
write rule, $s_\sym \rightarrow_\mathit{FW} s_\sym^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:sym}.

@@

\begin{lemma}[$\rcom$ preserves heap determinism]
\label{lem:J-determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
Javalite relation, $s_\sym \rcom s_\sym^\prime$, is
also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rcom$ in \figref{fig:javalite-common}.

@@

\begin{theorem}[$\rsym$ preserves heap well-formedness]
\label{thm:determ}
Given a state, $s_\sym$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(s_\sym)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(s_\sym^\prime)$, in any state related by the
symbolic relation, $s_\sym \rsym s_\sym^\prime$, is
also deterministic.
\end{theorem}
\begin{proof}
Proof by \lemref{lem:FA-determ}, \lemref{lem:FW-determ}, and \lemref{lem:J-determ}
which represent all the rules that relate states in
$\rsym$.
\end{proof}

%\begin{lemma}[Exactness of Reference Compare Rule]
%\label{lem:compare}
%If there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$, then:
%\begin{equation}
%\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
%\end{equation}
%\end{lemma}

\begin{lemma}[\textrm{E{\footnotesize QUALS}} ] preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{E}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

There are two rules that apply to state $s_\sym \in 2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch. 
\begin{proof}
Assume there exists states $s_\gse$ and $s_\sym$ such that $s_\sym \in \mathcal{RC}$ and $s_\gse \sqsubset s_\sym$. Let $s_\sym^\prime$ be any state such that $s_\sym \rsym s_\sym$ and let $\zeta_T = \forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime )$. Since $s_\gse \sqsubset s_\sym$, we know that $s_\gse \in \mathcal{RC}$, and that there exists a homomorphism $s_\gse \rightharpoonup_{h} s_\sym$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(s_\gse \rightharpoonup_{h} s_\sym) ) $. We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$ as follows: Let
$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gse\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
and let
$$\zeta_f = \zeta_T \setminus \zeta_t$$

Furthermore, there are two possible configurations for $s_\sym^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $. We now consider the partitions of $\zeta_T$ and configurations of $s_\sym^\prime$ in separate cases.

Case 1: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$. 
Compute state $s_\gse^\prime$ such that $s_\gse \rgse s_\gse^\prime$. In this case, the GSE ``equals - references true" rule applied, therefore $s_\gse^\prime$ is in $\zeta_t$. Observe that by applying Theorem~\ref{thm:mutex}, $\phi_\sym^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_\sym$. Therefore, $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) ) $ is true, and by extension, $s_\gse^\prime \sqsubset s_\sym^\prime$. Since this relation holds for arbitrary $s_\gse^\prime \in \zeta_t$, we now know that 
\begin{equation}
\label{eqn:RCForwardsTrue}
((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
\end{equation}

Case 2:  Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''. Since $\cfgnt{L}_\sym$ and $\cfgnt{R}_\sym$ are unchanged from $s_\sym$, and $\phi_\sym^\prime$ is only a strengthened version of $\phi_\sym$,  we know that
\begin{equation}
\label{eqn:RCSubset}
\{s_\gse^\prime | s_\gse^\prime \sqsubset s_\sym^\prime \} \subseteq \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym \rp \wedge s_\gse \rsym s_\gse^\prime\}
\end{equation}
Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset s_\sym^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
$$s_i^\prime \in \{s_\gse^\prime | \exists s_\gse \lp s_\gse \sqsubset s_\sym\rp \wedge s_\gse \rsym s_\gse^\prime\}$$ 
Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$. Because of this, and because of Theorem~\ref{thm:mutex}, we know that either all constraints in the set
$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp\}$$ are unsatisfiable, or that at least one constraint in the set
$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $s_\sym^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
\begin{equation}
\label{eqn:RCBackwardsTrue}
((s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (s_\gse^\prime \sqsubset s_\sym^\prime)) \Rightarrow s_\gse^\prime \in \zeta_t
\end{equation}

Case 3: Assume that $\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp$.
This means that the GSE ``equals - references false" rule applies. The proof for the ``equals - references false" rule is highly similar to the proof for Case 1, so we omit it for the sake of brevity. The result for this case is:
\begin{equation}
\label{eqn:RCForwardsFalse}
((\cfgnt{L}_\gse \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gse \lp \cfgnt{r}_1 \rp) \wedge (s_\gse^\prime \in \zeta_t)) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime
\end{equation}

Case 4: Assume that $s_\sym^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
The proof for this case is highly similar to the proof for Case 2, so we omit it for the sake of brevity. The result for this case is:
\begin{equation}
\label{eqn:RCBackwardsFalse}
s_\sym^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge s_\gse^\prime \sqsubset s_\sym^\prime \Rightarrow s_\gse^\prime \in \zeta_f
\end{equation}

Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine Equation \ref{eqn:RCForwardsTrue} with \ref{eqn:RCForwardsFalse} to find that 
\begin{equation}
\forall s_\gse^\prime ( s_\gse \rgse s_\gse^\prime \Rightarrow \exists s_\sym^\prime( (s_\sym \rsym s_\sym^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
Likewise, we can combine Equation \ref{eqn:RCBackwardsTrue} with Equation \ref{eqn:RCBackwardsFalse} to find that
\begin{equation}
\forall s_\sym^\prime ( s_\sym \rsym s_\sym^\prime\Rightarrow \exists s_\gse^\prime( (s_\gse \rgse s_\gse^\prime )\wedge (s_\gse^\prime\ \sqsubset\ s_\sym^\prime ))  )
\end{equation}
\end{proof}

>>>>

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation.  A bisimulation is a relation over pairs of states such that whenever two states, $\gsest$ and
$\symst$, are related in the bisimulation, $\gsest \sqsubset
\symst$, every successor, from either state, $\gsest
\rgse \gsest^\prime$ or $\symst \rsym
\symst^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $\gsest^\prime \sqsubset \symst^\prime$.

@@

%\begin{theorem}
%If exists state $\symst$ and set of states $\Gsest$ such that \eqnref{eqn:BisimulationForwards} and \eqnref{eqn:BisimulationBackwards} are satisfied, then:
%$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
%\label{}
%\end{theorem}

%\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
%\label{lem:init}
%If $\symst \cong \mathbb{FS}(\rightarrow_{\phi},s_0,\pi_n)$ for symbolic state $\symst = \lp \cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \phi_\sym\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$, initial state $s_0$, and control flow path $\pi_n$, and if there exists some intermediate state state $\symst^\prime$ such that $(\cfgnt{L}_\sym\ \cfgnt{R}_{s}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C}) \rsum^* (\cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \cfgnt{r}\ \cfgnt{f} \ \cfgnt{C})$, then:
% $$\symst^\prime \cong \{\forall \gsest^\prime | \exists \gsest (\gsest \sqsubset \symst \wedge (\gsest \rinit^* \gsest^\prime) ) \}$$
%\end{lemma}

@@

Now, to prove the reverse direction, choose any state $\gsest^\prime$ such that $\gsest^\prime \sqsubset q^\prime$. Since $\gsest^\prime \sqsubset q^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $\gsest^\prime \rightharpoonup_{h^\prime} q^\prime$, and that $\mathbb{S}( \phi_\gsest^\prime \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h^\prime} q^\prime) )$. From state $\gsest^\prime$, construct state $\gsest$ such that 
\begin{align*}
\gsest &= \lp \cfgnt{L}_\gsest\ \cfgnt{R}_\gsest\ \phi_\gsest\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
L_\gsest &= L_{\gsest^\prime} \setminus \{\cfgnt{r}^\prime \}\\
R_\gsest &= R_{\gsest^\prime}\\
\phi_\gsest &= \phi_\gsest^\prime
\end{align*}
Observe that by virtue of the GSE Field Access rule, $\gsest \rgse \gsest^\prime$. Now, construct function $h_\gsest$ so that $h_\gsest = h^\prime$. Observe that by Definition~\ref{def:homomorphism} $\gsest \rightharpoonup_{h_\gsest} q$,  and that $\mathbb{S}( \phi_\gsest \wedge \mathbb{HC}(\gsest \rightharpoonup_{h_\gsest} q) )$, so $\gsest \sqsubset q$. Therefore:
\begin{equation}
\forall q^\prime ( q \rsym q^\prime\Rightarrow \exists \Gsest^\prime( (\Gsest \rsgse \Gsest^\prime )\wedge (\Gsest^\prime\ \sqsubset\ q^\prime ))  )
\end{equation}
By \defref{bisimulation}, we conclude:
$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
\end{proof}

%proof for field write
%\begin{lemma}[Exactness of Field Write Rule]
%\label{lem:write}
%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{FW}$ and $\gsest \sqsubset \symst$, then:
%\begin{equation}
%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
%\end{lemma}

@@

By \defref{bisimulation}, we conclude:
$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$

@@

\begin{lemma}[$\rightarrow_\mathit{FA}$ preserves heap determinism]
\label{lem:FA-determ}
Given a state, $s$, with a deterministic heap,
$(\cfgnt{L}\ \cfgnt{R}) =
\mathrm{heap}(s)$, the new heap,
$(\cfgnt{L}^\prime\ \cfgnt{R}^\prime) =
\mathrm{heap}(s^\prime)$, in any state related by the field
access rule, $s \rightarrow_\mathit{FA} s^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FA}$ in \figref{fig:fHeap}.

@@

\begin{lemma}[$\rightarrow_\mathit{FW}$ preserves heap determinism]
\label{lem:FW-determ}
Given a state, $\symst$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(\symst)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(\symst^\prime)$, in any state related by the field
write rule, $\symst \rightarrow_\mathit{FW} \symst^\prime$,
is also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rightarrow_\mathit{FW}$ in \figref{fig:fHeap}.

@@

\begin{lemma}[$\rcom$ preserves heap determinism]
\label{lem:J-determ}
Given a state, $\symst$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(\symst)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(\symst^\prime)$, in any state related by the
Javalite relation, $\symst \rcom \symst^\prime$, is
also deterministic.
\end{lemma}
\begin{proof}
Proof by definition of $\rcom$ in \figref{fig:javalite-common}.

@@

\begin{theorem}[$\rsym$ preserves heap well-formedness]
\label{thm:determ}
Given a state, $\symst$, with a deterministic heap,
$(\cfgnt{L}_\sym\ \cfgnt{R}_\sym) =
\mathrm{heap}(\symst)$, the new heap,
$(\cfgnt{L}_\sym^\prime\ \cfgnt{R}_\sym^\prime) =
\mathrm{heap}(\symst^\prime)$, in any state related by the
symbolic relation, $\symst \rsym \symst^\prime$, is
also deterministic.
\end{theorem}
\begin{proof}
Proof by \lemref{lem:FA-determ}, \lemref{lem:FW-determ}, and \lemref{lem:J-determ}
which represent all the rules that relate states in
$\rsym$.
\end{proof}

%\begin{lemma}[Exactness of Reference Compare Rule]
%\label{lem:compare}
%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{RC}$ and $\gsest \sqsubset \symst$, then:
%\begin{equation}
%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
%\end{lemma}

\begin{lemma}[\textrm{E{\footnotesize QUALS}} ] preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{E}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:compare}
$$
\forall P \in 2^{S_\mathit{E}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

There are two rules that apply to states in $2^{E}$, one for the $\cfgt{true}$ branch and one for the $\cfgt{false}$ branch. Since the proofs for both rules are nearly identical, for brevity we will only show the proofs for the case for the $\cfgt{true}$ branch. 
\begin{proof}
Assume there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{RC}$ and $\gsest \sqsubset \symst$. Let $\symst^\prime$ be any state such that $\symst \rsym \symst$ and let $\zeta_T = \forall \gsest^\prime ( \gsest \rgse \gsest^\prime )$. Since $\gsest \sqsubset \symst$, we know that $\gsest \in \mathcal{RC}$, and that there exists a homomorphism $\gsest \rightharpoonup_{h} \symst$ such that $\mathbb{S}( \phi_\sym \wedge \mathbb{HC}(\gsest \rightharpoonup_{h} \symst) ) $. We partition $\zeta_T$ based on the values of $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp$ and $\cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$ as follows: Let
$$\zeta_t = \zeta_T \setminus \{ s_f | (s_f= \lp \cfgnt{L}_f\ \cfgnt{R}_f\ \phi_\gsest\ \eta\ \cfgnt{e}\ \cfgnt{k}\rp) \wedge (\cfgnt{L}_f \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_f \lp \cfgnt{r}_1 \rp ) \}$$
and let
$$\zeta_f = \zeta_T \setminus \zeta_t$$

Furthermore, there are two possible configurations for $\symst^\prime$: $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $ and $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $. We now consider the partitions of $\zeta_T$ and configurations of $\symst^\prime$ in separate cases.

Case 1: Assume that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$. 
Compute state $\gsest^\prime$ such that $\gsest \rgse \gsest^\prime$. In this case, the GSE ``equals - references true" rule applied, therefore $\gsest^\prime$ is in $\zeta_t$. Observe that by applying Theorem~\ref{thm:determ}, $\phi_\sym^\prime \wedge \phi_0 \wedge \phi_1$ reduces to $\phi_\sym$. Therefore, $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(\gsest^\prime \rightharpoonup_{h} \symst^\prime) ) $ is true, and by extension, $\gsest^\prime \sqsubset \symst^\prime$. Since this relation holds for arbitrary $\gsest^\prime \in \zeta_t$, we now know that 
\begin{equation}
\label{eqn:RCForwardsTrue}
((\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp) \wedge (\gsest^\prime \in \zeta_t)) \Rightarrow \gsest^\prime \sqsubset \symst^\prime
\end{equation}

Case 2:  Assume that $\symst^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp $, and define $\theta_\alpha$, $\theta_0$ and $\theta_1$ as in the ``equals (references-true) rule''. Since $\cfgnt{L}_\sym$ and $\cfgnt{R}_\sym$ are unchanged from $\symst$, and $\phi_\sym^\prime$ is only a strengthened version of $\phi_\sym$,  we know that
\begin{equation}
\label{eqn:RCSubset}
\{\gsest^\prime | \gsest^\prime \sqsubset \symst^\prime \} \subseteq \{\gsest^\prime | \exists \gsest \lp \gsest \sqsubset \symst \rp \wedge \gsest \rsym \gsest^\prime\}
\end{equation}
Suppose that there exists state $s_i^\prime$ such that $s_i^\prime \sqsubset \symst^\prime$ and $s_i^\prime \notin \zeta_t$. Because of Equation \ref{eqn:RCSubset}, we know that 
$$s_i^\prime \in \{\gsest^\prime | \exists \gsest \lp \gsest \sqsubset \symst\rp \wedge \gsest \rsym \gsest^\prime\}$$ 
Combining this with the assumption that $s_i^\prime \notin \zeta_t$, we must conclude that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp \neq  \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$. Because of this, and because of Theorem~\ref{thm:determ}, we know that either all constraints in the set
$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \theta_\alpha)\wedge \phi_i = \lp\phi_\alpha \wedge \phi_0 \wedge \phi_1\rp\}$$ are unsatisfiable, or that at least one constraint in the set
$$\{\phi_i \mid \exists \phi_\alpha (\phi_\alpha \in \lp \theta_0 \cup \theta_1 \rp)\wedge \lp \phi_i = \phi_\alpha \wedge \phi_0 \wedge \phi_1 \rp\}$$ 
is valid. Either way, $\mathbb{S}\lp\phi_i^\prime \wedge\phi_0\wedge \phi_1\rp$ is false and $\symst^\prime$ does not represent $s_i^\prime$. We have a contradiction. Therefore: 
\begin{equation}
\label{eqn:RCBackwardsTrue}
((\symst^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp) \wedge (\gsest^\prime \sqsubset \symst^\prime)) \Rightarrow \gsest^\prime \in \zeta_t
\end{equation}

Case 3: Assume that $\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp \neq \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp$.
This means that the GSE ``equals - references false" rule applies. The proof for the ``equals - references false" rule is highly similar to the proof for Case 1, so we omit it for the sake of brevity. The result for this case is:
\begin{equation}
\label{eqn:RCForwardsFalse}
((\cfgnt{L}_\gsest \lp \cfgnt{r}_0\rp = \cfgnt{L}_\gsest \lp \cfgnt{r}_1 \rp) \wedge (\gsest^\prime \in \zeta_t)) \Rightarrow \gsest^\prime \sqsubset \symst^\prime
\end{equation}

Case 4: Assume that $\symst^\prime$ has the form $\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp $.
The proof for this case is highly similar to the proof for Case 2, so we omit it for the sake of brevity. The result for this case is:
\begin{equation}
\label{eqn:RCBackwardsFalse}
\symst^\prime=\lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp \wedge \gsest^\prime \sqsubset \symst^\prime \Rightarrow \gsest^\prime \in \zeta_f
\end{equation}

Since $\zeta_T = \zeta_t \cup \zeta_f$, we can combine Equation \ref{eqn:RCForwardsTrue} with \ref{eqn:RCForwardsFalse} to find that 
\begin{equation}
\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
\end{equation}
Likewise, we can combine Equation \ref{eqn:RCBackwardsTrue} with Equation \ref{eqn:RCBackwardsFalse} to find that
\begin{equation}
\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
\end{equation}
By \defref{bisimulation}, we conclude:
$$(\Gsest \ \symst) \in F_\sim(\sqsubset)$$
\end{proof}

%\begin{lemma}[Exactness of New Rule]
%\label{lem:new}
%If there exists states $\gsest$ and $\symst$ such that $\symst \in \mathcal{NW}$ and $\gsest \sqsubset \symst$, then:
%\begin{equation}
%\forall \gsest^\prime ( \gsest \rgse \gsest^\prime \Rightarrow \exists \symst^\prime( (\symst \rsym \symst^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
%and
%\begin{equation}
%\forall \symst^\prime ( \symst \rsym \symst^\prime\Rightarrow \exists \gsest^\prime( (\gsest \rgse \gsest^\prime )\wedge (\gsest^\prime\ \sqsubset\ \symst^\prime ))  )
%\end{equation}
